Bayesian model comparison for rare variant association studies of multiple phenotypes

### 2018-01-15 tex/MVMetaLearnMRP2017OctoberMRPMM.tex
adding editing nature class that permits figure inclusion
Text updates

\documentclass{nature}
\usepackage[T1]{fontenc}
\usepackage[dvips]{graphicx}
\usepackage[usenames]{color}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amscd}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{eucal}
% Please add the following required packages to your document preamble:
 \usepackage{booktabs}
\usepackage{rotating}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{bbm}
\usepackage[font=small]{caption}
\usepackage[font=small]{subcaption}
\usepackage{color}
\usepackage{lineno}
\usepackage{url}
\usepackage{lscape}
\usepackage{breqn}
\usepackage{enumitem}
\usepackage{listings}
\def\bs{\boldsymbol}
\def\til{\widetilde}
\def\MM{\mathcal{M}}
\def\Vy{\widehat{\textrm{V}}_Y}

\bibliographystyle{naturemag}
\title{Bayesian model comparison for rare variant association studies of multiple phenotypes}
\author{Christopher DeBoever$^{1}$, Matthew Aguirre$^{1}$, Yosuke Tanigawa$^{1}$, Adam Lavertu$^{1}$, Greg McInnes$^{1}$, Timothy Poterba$^{2}$, Mark J. Daly$^{2,3}$,  Matti Pirinen$^{4}$\thanks{matti.pirinen@helsinki.fi}, and Manuel A. Rivas$^{1}$\thanks{mrivas@stanford.edu}}
\usepackage{setspace}   
\linenumbers
\begin{document}
\maketitle
\begin{abstract}
\singlespacing
Whole genome sequencing studies applied to large populations or biobanks with extensive phenotyping raise new analytic challenges. The need to consider many variants at a locus or group of genes simultaneously and the potential to study many correlated phenotypes with shared genetic architecture provide opportunities for discovery and inference that are not addressed by the traditional one variant-one phenotype association study. Here we introduce a model comparison approach we refer to as MRP for rare variant association studies that considers correlation, scale, and location of genetic effects across a group of genetic variants, phenotypes, and studies. In so doing we consider the use of summary statistic data to 1) apply standard univariate and multivariate gene-based meta-analysis models, 2) models for assessing heterogeneity of genetic effects, which may be used in practice for downstream quality control, and 3) models for identifying protective protein-truncating variants, which can expedite drug discovery.  Through simulation studies, we demonstrate that the proposed model comparison approach may improve ability to detect rare variant association signals. Finally, we demonstrate its use with rare variant data combined with asthma diagnosis and haematological and spirometry measures for individuals in the UK Biobank. We show that we are able to retain useful features from widely-used meta-analysis approaches and prioritize protective modifiers of disease risk.
\end{abstract}

@@

%%Apply methods to the GLGC data and exome sequencing data sets. 
We apply MRP to four phenotypes: asthma (HC382: the corresponding phenotype label in Global Biobank Engine [\url{https://biobankengine.stanford.edu}]), eosinophil count (INI30150), Forced Expiratory Volume in 1-second (FEV1, INI3063), and Forced Vital Capacity (FVC, INI3062) in the UK Biobank dataset. We show that we are able to retain useful features from single variant and single phenotype meta-analysis, rare variant analysis, and prioritize protective modifiers of disease risk.

%% FIGURE 1 
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{../figures/FIG1FINAL.pdf}
  \caption{Schematic overview of MRP. A. MRP is suitable for a broad range of rare variant association study designs including (from left to right): i) case-control, ii) multiple diseases with shared controls, iii) single quantitative phenotype, and iv) mixture of case-control and quantitative phenotypes. B. Diagram of factors considered in rare variant association analysis including the correlation matrices: $\mathbf{R_{\textrm{study}}}$  (expected correlation of genetic effects among a group of studies), $\mathbf{R_{\textrm{var}}}$ (expected correlation of genetic effects among a group of variants), and $\mathbf{R_{\textrm{phen}}}$ (expected correlation of genetic effects among a group of phenotypes); the scale parameter for genetic variant annotation; and the location of genetic effects, which may be used to prioritize or identify protective modifiers of disease risk.}
  \label{Fig1}
  \end{figure}

@@

\newpage 
%% FIGURE 2
\begin{figure}
\centering
   \includegraphics[width=\textwidth]{../figures/Figure2Nov2017.pdf}
  \caption{Simulation studies. A. Comparison of $-\log_{10}$(p-values) from frequentist $\textrm{BF}_{\textrm{MRP}}$ approximation for an independent effects and a similar effects model to commonly used gene-based statistical tests (skat and burden). B. Comparison of log10(Bayes Factors) obtained when raw genotype and phenotype data is available to a scenario where summary statistics only was available and similar effects across studies is assumed. C. From single variant and single phenotype to multiple variants and multiple phenotypes gene discovery: ROC curves for detecting gene association to any of the phenotypes using single variant/single phenotype association (blue) to multiple variants and multiple phenotypes association (purple). D. ROC curves for detecting gene association when incorporating prior mean of genetic effects (orange) to identify protective alleles. }
  \label{Fig2}
\end{figure}

@@

\subsubsection{Model comparison applied to asthma, eosinophil count, forced expiratory volume in 1-second, and forced vital capacity summary statistic data}
We applied the MRP model comparison approach to summary statistic data for coding variants on the UK Biobank array. The summary statistic data was generated from single variant logistic regression and linear regression analysis applied to asthma, eosinophil count, forced expiratory volume in 1-second, and forced vital capacity phenotypes. We applied the model to missense variants and PTVs for each phenotype separately (\ref{Fig3}A-D) as well as to all phenotypes jointly (\ref{Fig3}E) and obtained $\log_{10}$ BF for each gene. We observed evidence that missense variants and PTVs in \textit{IL33} affect eosinophil counts and offer protection from asthma from the single-phenotype analyses\cite{DeBoever179762, 10.1371/journal.pgen.1006659}, though the evidence of association was strongest for the joint analysis (\ref{Tab1}). We also found evidence for associations between missense variants and PTVs in several other genes and the four phenotypes in the joint model that were not identified when considering asthma alone. For instance, \textit{GPR20}, \textit{CSF2RB}, \textit{PACS2}, and \textit{CCR3} all had $\log_{10}$ BF greater than 9 in the eosinophil count-only analysis but $\log_{10}$ BF less than 0 for the asthma-only analysis. In the joint model, the $\log_{10}$ BFs for these genes were all greater than six indicating possible associations with these traits. Besides \textit{IL33}, none of the genes with $\log_{10}$ BF greater than six in the joint model were reported in a large GWAS for allergic disease including asthma\cite{Ferreira:2017ba} though \textit{CCR3} is near a locus associated with atopy in a previous meta-analysis\cite{Ober:2011jk}. These results illustrate the ability of applying model comparison to multiple traits simultaneously to identify new genes involved in disease.

%% FIGURE 3
\begin{figure}
\centering
\includegraphics[width=\textwidth]{../figures/manhattan.pdf}
  \caption{$\log_{10}$ Bayes Factors from applying MRP to summary statistics for missense and protein-truncating variants from (A) eosinophil counts (INI30150), (B) forced vital capacity (FVC, INI3062), (C) forced expiratory volume in 1-second (FEV1, INI3063), (D) asthma (HC382), and (E) all four traits jointly. The four genes outside of chromosome 6 with the largest Bayes Factors are labeled in each plot. Only $\log_{10}$ Bayes Factors greater than -5 are plotted.}
  \label{Fig3}
\end{figure}

%% TABLE 3
\begin{table}
\begin{tabular}{llllll}
\toprule
{} & Joint & Eosinophil count &   FVC &  FEV1 & Asthma \\
\midrule
\textit{IL33}   &  36.6 &             31.5 &  -2.3 &  -1.9 &    9.4 \\
\textit{GPR20}  &  10.2 &             10.4 &  -0.1 &  -0.2 &        \\
\textit{ZFAT}   &  10.1 &             -3.1 &   7.8 &   5.9 &   -0.5 \\
\textit{CSF2RB} &   9.0 &              9.1 &   0.2 &  -0.1 &   -0.2 \\
\textit{SCMH1}  &   7.1 &             -1.5 &   6.8 &   2.6 &   -0.9 \\
\textit{PACS2}  &   6.2 &              9.6 &  -1.3 &  -1.6 &   -0.5 \\
\textit{CCR3}   &   6.0 &             14.0 &  -3.3 &  -3.7 &   -1.0 \\
\textit{ELN}    &   5.0 &             -1.5 &   4.9 &   2.3 &   -0.6 \\
\bottomrule
\end{tabular}
\caption{$\log_{10}$ Bayes Factors for genes outside of chromosome 6 with $\log_{10}$ Bayes Factors greater than 5 in the joint analysis.}
\label{Tab1}
\end{table}

\section{Discussion}
In this study, we developed a Bayesian model comparison approach MRP that shares information across both variants and phenotypes to identify rare variant associations. We used simulations to compare MRP to the widely used burden and SKAT tests for identifying rare variant associations and found that jointly considering both variants and phenotypes can improve the ability to detect associations. We also applied the MRP model comparison framework to summary statistic data from four traits from the UK Biobank: asthma, eosinophil counts, forced expiratory volume in 1-second (FEV1), and forced vital capacity (FVC). We identified strong evidence for the previously described association between \textit{IL33} and asthma\cite{DeBoever179762, 10.1371/journal.pgen.1006659} as well as evidence of association for several additional genes that have not been previously reported \ref{Tab1}.

@@

\subsubsection{UK Biobank Asthma Application}
For the Manhattan plots \ref{Fig3} and table \ref{Tab1}, we removed any genes with non-unique gene symbols. We also removed the sense overlapping gene \textit{CTD-3064M3.3} and and the antisense gene \textit{ZFAT-AS1} since these genes overlap \textit{GPR20} and \textit{ZFAT} respectively and therefore have the same $\log_{10}$ Bayes Factors as those genes.

@@

@@

\subsection{Implementation details: HDF5 tables}
Although summary statistics are quicker to read and process than raw data, the number of studies meta-analyzed in this work is expected to be sufficiently large to require optimizations in data representation and processing. Our solution was the use of the HDF5 (Hierarchical Data Format 5) data representation to enable rapid processing of effect size, uncertainty, and cross-trait estimate data. HDF5 is a fast and lightweight file format designed for scientific data. It has bindings for R, Python, C/C++, Java, and nearly every other population programming language. Reading data from a table within a HDF5 file can be an order of magnitude faster than reading text files from a Unix file, and it makes it easier to organize data within an internal structure.

%% FIGURE 3
\begin{figure}
\centering
\includegraphics[width=\textwidth]{../figures/hdf5MAMBAMRP.pdf}
  \caption{Our HDF5 implementation contained the following components: first, a group with one table per annotation file. All effect size (beta) values and study-specific annotations were contained here, and the number of tables is limited by $S\ \textrm{(the number of studies)} \times K\ \textrm{(the number of traits)}$. Second, a group with site-site covariance data. While these covariance matrices may have dimension $M\ \textrm{(the number of variants)} \times M$, we store the data as tables, each row specifiying the covariance between two variants. The number of tables should be the same as the previous set, capped by $S\ \textrm{(the number of studies)} \times K\ \textrm{(the number of traits)}$. Third, we store one table with sigma values for each study/phenotype combination. In the event that the traits were rank-normal transformation was performed these sigma values are equal to 1. These are used to compute correlation between two datasets. Finally, we store a matrix/table pair for Vy null and its index. The Vy null matrix has dimensions $ (S \times K) \times (S \times K)$ each entry specifying the estimated correlation of effect sizes between two datasets. The index table encodes row/column position of each dataset.}
  \label{hdf5}
\end{figure}

>>>>

\documentclass{nature}
\usepackage[T1]{fontenc}
\usepackage[usenames]{color}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amscd}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{eucal}
% Please add the following required packages to your document preamble:
 \usepackage{booktabs}
\usepackage{rotating}
\usepackage{graphicx}
\graphicspath{{../figures/}}
\usepackage{multirow}
\usepackage{bbm}
\usepackage[font=small]{caption}
\usepackage[font=small]{subcaption}
\usepackage{color}
\usepackage{lineno}
\usepackage{url}
\usepackage{lscape}
\usepackage{breqn}
\usepackage{enumitem}
\usepackage{listings}
\def\bs{\boldsymbol}
\def\til{\widetilde}
\def\MM{\mathcal{M}}
\def\Vy{\widehat{\textrm{V}}_Y}
\bibliographystyle{naturemag}
\title{Bayesian model comparison for rare variant association studies of multiple phenotypes}
\author{Christopher DeBoever$^{1}$, Matthew Aguirre$^{1}$, Yosuke Tanigawa$^{1}$, Timothy Poterba$^{2}$, Mark J. Daly$^{2,3}$,  Matti Pirinen$^{4}$\thanks{matti.pirinen@helsinki.fi}, and Manuel A. Rivas$^{1}$\thanks{mrivas@stanford.edu}}
\usepackage{setspace}   
\linenumbers

\begin{document}
\maketitle
\begin{abstract}
\singlespacing
Whole genome sequencing studies applied to large populations or biobanks with extensive phenotyping raise new analytic challenges. The need to consider many variants at a locus or group of genes simultaneously and the potential to study many correlated phenotypes with shared genetic architecture provide opportunities for discovery and inference that are not addressed by the traditional one variant-one phenotype association study. Here we introduce a model comparison approach we refer to as MRP for rare variant association studies that considers correlation, scale, and location of genetic effects across a group of genetic variants, phenotypes, and studies. In so doing we consider the use of summary statistic data to 1) apply standard univariate and multivariate gene-based meta-analysis models, 2) models for assessing heterogeneity of genetic effects, which may be used in practice for downstream quality control, and 3) models for identifying protective protein-truncating variants, which can expedite drug discovery.  Through simulation studies, we demonstrate that the proposed model comparison approach may improve ability to detect rare variant association signals. Finally, we demonstrate its use with rare variant data combined with asthma diagnosis and haematological and spirometry measures for individuals in the UK Biobank. We show that we are able to retain useful features from widely-used meta-analysis approaches and prioritize protective modifiers of disease risk.
\end{abstract}

@@

%%Apply methods to the GLGC data and exome sequencing data sets. 
We also apply MRP to two groups of related phenotypes. First, we apply MRP to asthma (HC382: the corresponding phenotype label in Global Biobank Engine [\url{https://biobankengine.stanford.edu}]), eosinophil count (INI30150), Forced Expiratory Volume in 1-second (FEV1, INI3063), and Forced Vital Capacity (FVC, INI3062) in the UK Biobank dataset. We next apply MRP to glaucoma (HC276), intra-ocular pressure (INI5263), and corneal resistance factor (INI5265). We show that we are able to retain useful features from single variant and single phenotype meta-analysis, rare variant analysis, and prioritize protective modifiers of disease risk.

%% FIGURE 1 
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{FIG1FINAL.pdf}
  \caption{Schematic overview of MRP. A. MRP is suitable for a broad range of rare variant association study designs including (from left to right): i) case-control, ii) multiple diseases with shared controls, iii) single quantitative phenotype, and iv) mixture of case-control and quantitative phenotypes. B. Diagram of factors considered in rare variant association analysis including the correlation matrices: $\mathbf{R_{\textrm{study}}}$  (expected correlation of genetic effects among a group of studies), $\mathbf{R_{\textrm{var}}}$ (expected correlation of genetic effects among a group of variants), and $\mathbf{R_{\textrm{phen}}}$ (expected correlation of genetic effects among a group of phenotypes); the scale parameter for genetic variant annotation; and the location of genetic effects, which may be used to prioritize or identify protective modifiers of disease risk.}
  \label{Fig1}
  \end{figure}

@@

\newpage 
%% FIGURE 2
\begin{figure}
\centering
   \includegraphics[width=\textwidth]{Figure2Nov2017.pdf}
  \caption{Simulation studies. A. Comparison of $-\log_{10}$(p-values) from frequentist $\textrm{BF}_{\textrm{MRP}}$ approximation for an independent effects and a similar effects model to commonly used gene-based statistical tests (skat and burden). B. Comparison of log10(Bayes Factors) obtained when raw genotype and phenotype data is available to a scenario where summary statistics only was available and similar effects across studies is assumed. C. From single variant and single phenotype to multiple variants and multiple phenotypes gene discovery: ROC curves for detecting gene association to any of the phenotypes using single variant/single phenotype association (blue) to multiple variants and multiple phenotypes association (purple). D. ROC curves for detecting gene association when incorporating prior mean of genetic effects (orange) to identify protective alleles. }
  \label{Fig2}
\end{figure}

@@

\subsubsection{Model comparison applied to summary statistic from the UK Biobank}
We applied the MRP model comparison approach to summary statistic data generated from single variant logistic regression and linear regression analysis for coding variants on the UK Biobank array (Methods). We first applied MRP to the asthma, eosinophil count, forced expiratory volume in 1-second, and forced vital capacity phenotypes. We applied the model to missense variants and PTVs for each phenotype separately (Fig.~\ref{asthma}A-D) as well as to all phenotypes jointly (Fig.~\ref{asthma}E) and obtained $\log_{10}$ BF for each gene. As expected from recent studies \cite{DeBoever179762, 10.1371/journal.pgen.1006659}, we observed evidence that missense variants and PTVs in \textit{IL33} affect eosinophil counts and offer protection from asthma from the single-phenotype analyses, though the evidence of association was strongest for the joint analysis (Table~\ref{asthma_table}). We also found evidence for associations between missense variants and PTVs in several other genes and the four phenotypes in the joint model that were not identified when considering asthma alone. For instance, \textit{GPR20}, \textit{CSF2RB}, \textit{PACS2}, and \textit{CCR3} all had $\log_{10}$ BF greater than 9 in the eosinophil count-only analysis but $\log_{10}$ BF less than 0 for the asthma-only analysis. In the joint model, the $\log_{10}$ BFs for these genes were all greater than six indicating possible associations with these traits. Besides \textit{IL33}, none of the genes with $\log_{10}$ BF greater than six in the joint model were reported in a large GWAS for allergic disease including asthma\cite{Ferreira:2017ba} though \textit{CCR3} is near a locus associated with atopy in a previous meta-analysis\cite{Ober:2011jk}.

We also applied MRP to missense variants and PTVs for glaucoma, intra-ocular pressure, and corneal resistance factor as well as performing a joint analysis and a joint analysis focused on protective associations. While the individual glaucoma analysis did not yield any associations with $\log_{10}$ BF greater than 5, the joint analyses identified missense and PTVs in both \textit{ANGPTL7} and \textit{WNT10A} as associated with protection against glaucoma. These results illustrate the ability of applying model comparison to multiple traits simultaneously to identify protective modifiers of disease.

%% FIGURE 3
\begin{figure}
\centering
\includegraphics[width=\textwidth]{glaucoma_manhattan.pdf}
  \caption{$\log_{10}$ Bayes Factors from applying MRP to summary statistics for missense and protein-truncating variants from (A) glaucoma (HC276), (B) intra-ocular pressure (INI5263), (C) corneal resistance factor (INI5265), and (D) all three traits jointly. (E) shows the results of a joint analysis focused on finding rare variants that protect against glaucoma. The genes outside of chromosome 6 with with Bayes Factor greater than three are indicated by arrows. Only $\log_{10}$ Bayes Factors greater than zero are plotted.}
  \label{glaucoma}
\end{figure}

\section{Discussion}
In this study, we developed a Bayesian model comparison approach MRP that shares information across both variants and phenotypes to identify rare variant associations. We used simulations to compare MRP to the widely used burden and SKAT tests for identifying rare variant associations and found that jointly considering both variants and phenotypes can improve the ability to detect associations. We also applied the MRP model comparison framework to summary statistic data from four traits from the UK Biobank: asthma, eosinophil counts, forced expiratory volume in 1-second (FEV1), and forced vital capacity (FVC). We identified strong evidence for the previously described association between \textit{IL33} and asthma\cite{DeBoever179762, 10.1371/journal.pgen.1006659} as well as evidence of association for several additional genes that have not been previously reported (Table~\ref{asthma_table}).

@@

\subsubsection{UK Biobank Asthma Application}
For the Manhattan plots and Table \ref{asthma_table}, we removed any genes with non-unique gene symbols. We also removed the sense overlapping gene \textit{CTD-3064M3.3} and and the antisense gene \textit{ZFAT-AS1} since these genes overlap \textit{GPR20} and \textit{ZFAT} respectively and therefore have the same $\log_{10}$ Bayes Factors as those genes.

@@

\subsection{Author Contributions}
M.A.R. and M.P. designed the method and derived all analytical calculations. M.A.R., M.P., and C.D. wrote the manuscript. Y.T., M.A., and C.D. provided analysis and designed figures. T.P. designed hDF5 tables and implementation of loaders. M.J.D. provided critical feedback on methodology.

\subsection{Acknowledgments}
This research has been conducted using the UK Biobank Resource under Application Number 24983. We thank all the participants in the UK Biobank study. M.A.R. and C.D. are supported by Stanford University and a National Institute of Health center for Multi- and Trans-ethnic Mapping of Mendelian and Complex Diseases grant (5U01 HG009080). C.D. is supported by a postdoctoral fellowship from the Stanford Center for Computational, Evolutionary, and Human Genomics and the Stanford ChEM-H Institute. Y .T. is supported by Funai Overseas Scholarship from Funai Foundation for Information Technology and the Stanford University Biomedical Informatics Training Program. The primary and processed data used to generate the analyses presented here are available in the UK Biobank access management system (https://amsportal.ukbiobank.ac.uk/) for application 24983, ?Generating effective therapeutic hypotheses from genomic and hospital linkage data? (http://www.ukbiobank.ac.uk/wp-content/uploads/2017/06/24983-Dr-Manuel-Rivas.pdf), and the results are displayed in the Global Biobank Engine (https://biobankengine.stanford.edu). We would like to thank the Customer Solutions Team from Paradigm4 who helped us implement efficient databases for queries and application of inference methods to the data, and also implemented optimized versions of truncated singular value decomposition. M.A.R. is a paid consultant in Genomics PLC.

@@

\subsection{Implementation details: HDF5 tables}
Although summary statistics are quicker to read and process than raw data, the number of studies meta-analyzed in this work is expected to be sufficiently large to require optimizations in data representation and processing (Figure \ref{hdf5}). Our solution was the use of the HDF5 (Hierarchical Data Format 5) data representation to enable rapid processing of effect size, uncertainty, and cross-trait estimate data. HDF5 is a fast and lightweight file format designed for scientific data. It has bindings for R, Python, C/C++, Java, and nearly every other population programming language. Reading data from a table within a HDF5 file can be an order of magnitude faster than reading text files from a Unix file, and it makes it easier to organize data within an internal structure.

 %% FIGURE: ASTHMA MANHATTAN
\begin{figure}
\centering
\includegraphics[width=\textwidth]{asthma_manhattan.pdf}
  \caption{$\log_{10}$ Bayes Factors from applying MRP to summary statistics for missense and protein-truncating variants from (A) eosinophil counts (INI30150), (B) forced vital capacity (FVC, INI3062), (C) forced expiratory volume in 1-second (FEV1, INI3063), (D) asthma (HC382), and (E) all four traits jointly. The four genes outside of chromosome 6 with the largest Bayes Factors are labeled in each plot. Only $\log_{10}$ Bayes Factors greater than -5 are plotted.}
  \label{asthma}
\end{figure}

%% TABLE 3
\begin{table}
\begin{tabular}{llllll}
\toprule
{} & Joint & Eosinophil count &   FVC &  FEV1 & Asthma \\
\midrule
\textit{IL33}   &  36.6 &             31.5 &  -2.3 &  -1.9 &    9.4 \\
\textit{GPR20}  &  10.2 &             10.4 &  -0.1 &  -0.2 &        \\
\textit{ZFAT}   &  10.1 &             -3.1 &   7.8 &   5.9 &   -0.5 \\
\textit{CSF2RB} &   9.0 &              9.1 &   0.2 &  -0.1 &   -0.2 \\
\textit{SCMH1}  &   7.1 &             -1.5 &   6.8 &   2.6 &   -0.9 \\
\textit{PACS2}  &   6.2 &              9.6 &  -1.3 &  -1.6 &   -0.5 \\
\textit{CCR3}   &   6.0 &             14.0 &  -3.3 &  -3.7 &   -1.0 \\
\textit{ELN}    &   5.0 &             -1.5 &   4.9 &   2.3 &   -0.6 \\
\bottomrule
\end{tabular}
\caption{$\log_{10}$ Bayes Factors for genes outside of chromosome 6 with $\log_{10}$ Bayes Factors greater than 5 in the joint analysis.}
\label{asthma_table}
\end{table}

%% FIGURE 3
\begin{figure}
\centering
\includegraphics[width=\textwidth]{hdf5MAMBAMRP.pdf}
  \caption{Our HDF5 implementation contained the following components: first, a group with one table per annotation file. All effect size (beta) values and study-specific annotations were contained here, and the number of tables is limited by $S\ \textrm{(the number of studies)} \times K\ \textrm{(the number of traits)}$. Second, a group with site-site covariance data. While these covariance matrices may have dimension $M\ \textrm{(the number of variants)} \times M$, we store the data as tables, each row specifiying the covariance between two variants. The number of tables should be the same as the previous set, capped by $S\ \textrm{(the number of studies)} \times K\ \textrm{(the number of traits)}$. Third, we store one table with sigma values for each study/phenotype combination. In the event that the traits were rank-normal transformation was performed these sigma values are equal to 1. These are used to compute correlation between two datasets. Finally, we store a matrix/table pair for Vy null and its index. The Vy null matrix has dimensions $ (S \times K) \times (S \times K)$ each entry specifying the estimated correlation of effect sizes between two datasets. The index table encodes row/column position of each dataset.}
  \label{hdf5}
\end{figure}
